DeepSphere: a graph-based spherical CNN

### 2019-09-23 main.tex

\paragraph{Theoretical convergence.}
We extend the work of Belkin and Nyiogi to a fixed sampling.
Given a sampling $V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.

\begin{theorem}
	For a sampling $V = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\mathbb S^2|}{4\pi t_n}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\mathbb S^2}$  for $n\to\infty$:
	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n} \b{L}_n^{t_n} T_V f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.$$
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
This theorem implies immediately that $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation and hence is a strong hint for equivariance.
Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{...} inspires us in the construction of our graph Laplacian. It gives us a strong hint how the parameter $t$ needs to be adjusted with respect to the number of points $n$.

It is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
First, it is \emph{not} a proof of equivariance of the graph convolution for a specific sampling. To construct such a proof, a stronger convergence result is needed, for example uniform convergence (instead of pointwise).
Unfortunately, the graph laplacian does \emph{not} converges uniformly in general \cite{belkin2007convergence}. This can probably be overcome by considering a specific class of functions, such as bandlimited function.
Second, while do not have a proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}. This is discussed in Appendix~\ref{...}

>>>>

\paragraph{Theoretical convergence.}
We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme. 
Given a sampling scheme $V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
\begin{theorem}
	For a sampling $V = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\mathbb S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\mathbb S^2}$  for $n\to\infty$:
	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.$$
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
This theorem implies immediately that $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation and hence is a strong hint for equivariance.
Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{sec: appendix: proof of theorem} inspires us in the construction of our graph Laplacian. It gives us a strong hint how the parameter $t$ needs to be adjusted with respect to the number of points $n$.

It is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
First, it is \emph{not} a proof of equivariance of the graph convolution for a specific sampling. To construct such a proof, a stronger convergence result is needed, for example uniform convergence (instead of pointwise).
Unfortunately, the graph laplacian does \emph{not} converges uniformly in general \cite{belkin2007convergence}. This can probably be overcome by considering a specific class of functions, such as bandlimited function.
Second, while do not have a proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}. This is discussed in Appendix \ref{sec: appendix: proof of theorem}.
